### 2014-04-17 doc/uist14/iteration3.tex
made some final changes before submission

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_principle.png}
\caption{Even when the user's absolution position changes, the relative relationship in the orientation space remain invariant.}
\label{fig:third_principle}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique3.pdf}
\caption{\ben{figure in interactionModel2.key file.} Our third technique learned each target's absolute orientation and construct the orientation map. Though we store the absolute orientation value, during the {\em refinement} stage, the prediction is only based on relative changes to a reference point. Thus, the prediction will work regardless of user's position.}
\label{fig:third_technique}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_principle.png}
\caption{This illustrates that when the change of user's absolution position doesn't change the relative relationship of physical targets.}
\label{fig:third_principle}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique3.pdf}
\caption{Our third technique learned each target's absolute orientation and construct the adjacency map. During the {\em refinement} stage, the prediction is based on relative changes to a reference point.}
\label{fig:third_technique}
\end{figure}
